---
title: "Peer-graded-assignment"
author: "You Chen"
date: "12/17/2019"
output: html_document
---

#step 1:download and unzip dataser
```{r}
if(!file.exists("./data")){dir.create("./data")}
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
download.file(fileUrl,destfile="./data/Dataset.zip")

unzip(zipfile = "./data/Dataset.zip",exdir = "./data")
```

#reading training file
```{r}
features <- read.table('./data/UCI HAR Dataset/features.txt',col.names = c("n","functions"))

activities <-  read.table('./data/UCI HAR Dataset/activity_labels.txt',col.names = c("code","activity"))

x_train <- read.table("./data/UCI HAR Dataset/train/X_train.txt",col.names = features$functions)
y_train <- read.table("./data/UCI HAR Dataset/train/y_train.txt",col.names = "code")
subject_train <- read.table("./data/UCI HAR Dataset/train/subject_train.txt",col.names = "subject")

x_test <- read.table("./data/UCI HAR Dataset/test/X_test.txt",col.names = features$functions)
y_test<- read.table("./data/UCI HAR Dataset/test/y_test.txt",col.names = "code")
subject_test <- read.table("./data/UCI HAR Dataset/test/subject_test.txt",col.names = "subject")
```

#Step 1: Merges the training and the test sets to create one data set.
```{r}
X <- rbind(x_train,x_test)
Y <- rbind(y_train,y_test)
subject <- rbind(subject_train,subject_test)
merged_data <- cbind(subject,Y,X)
```

#step2 extract only the measures on the mean and standard deviation for each measurement.
```{r}
library(dplyr)
TidyData <- merged_data %>% select(subject,code,contains("mean"),contains("std"))
```

#step 3 replace descriptive activity values to name the activities in the data set
```{r}
TidyData$code <- activities[TidyData$code,2]
```

#step 4 appropriately labels the data set with descriptive variable names
```{r}
names(TidyData)[2]="activity"
names(TidyData) <-gsub("Acc","Accelerometer",names(TidyData))
names(TidyData)<-gsub("Gyro", "Gyroscope", names(TidyData))
names(TidyData)<-gsub("BodyBody", "Body", names(TidyData))
names(TidyData)<-gsub("Mag", "Magnitude", names(TidyData))
names(TidyData)<-gsub("^t", "Time", names(TidyData))
names(TidyData)<-gsub("^f", "Frequency", names(TidyData))
names(TidyData)<-gsub("tBody", "TimeBody", names(TidyData))
names(TidyData)<-gsub("-mean()", "Mean", names(TidyData), ignore.case = TRUE)
names(TidyData)<-gsub("-std()", "STD", names(TidyData), ignore.case = TRUE)
names(TidyData)<-gsub("-freq()", "Frequency", names(TidyData), ignore.case = TRUE)
names(TidyData)<-gsub("angle", "Angle", names(TidyData))
names(TidyData)<-gsub("gravity", "Gravity", names(TidyData))
```

#step 5 From the dataset in step 4, create a second,independent tidy data with the average of each variable for each activity and each subject.
```{r}
library(dplyr)
FinalData <- TidyData%>%
  group_by(subject,activity)%>%
  summarise_all(funs(mean))
write.table(FinalData,"FinalData.txt",row.names = FALSE)

```





